---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(ig)
```
# ig

> 🖼  A minimal R client for interacting with Instagram's public API.

## Installation

You can install **{ig}** from [Github](https://github.com) with:

```{r, eval = FALSE}
devtools::install_github("mkearney/ig")
```

## Authorization

To become authorized to interact with Instagram's API, users must first [go here and create an Instagram app](https://www.instagram.com/developer). Once you've created an app, copy the **`Client ID`** and **`Client Secret`** keys from the app's page and pass them along to `ig_create_token()`.

```{r, eval = FALSE}
## use client_id and client_secret to create and save access token
ig_create_token("pb112zgv5065tu60pxnqvp88f6hovbur", 
  "drz97x61d9s5g2nlcu87v63mdphiedcv")

## view your access token
ig_token()
```

The rest of the token process is automated for you (you don't need to reference it again).

## Endpoints

There are numerous API endpoints, but thanks to recent changes by Instagram, most users won't get access to large amounts of public data (at least not without first going through a strict submission process). Here are some that should still work though:

### `users/self`

```{r users_self}
## get your instagram data
me <- ig_users_self()

## view data
as_tbl(me)
```


### `users/self/media/recent`

```{r ig_users_self_media_recent}
## get your media data
my_media <- ig_users_self_media_recent()

## view data
as_tbl(my_media)
```

### `tags/{tags-name}`

```{r tags}
## get tags data
ig_tags <- ig_tags(tag = "metoo")

## view data
as_tbl(ig_tags)
```

### `tags/search`

```{r tags_search}
## search tags data
ig_tags <- ig_tags_search(q = "metoo")

## view data
as_tbl(ig_tags)
```
